### 2020-05-02 doctemp/assets/AlgebraicLoop/brokenloop.tex
Revised docs.

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        % Place the blocks 
        \draw pic (b1) {Component={Static\\System}{t}};
        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
        % Glow the blocks
        \drawshadowbis{b1-edge};
        \drawshadowbis{b2-edge};
        \drawshadowbis{b3-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
            \draw[->] (b1-edge.east) -- (b2-edge.west);
            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
            \draw[->] (a) -- ++(0.5cm, 0cm);
            \draw[->] (a) |- (b3-edge.east);
            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
            \draw[-] ([yshift=0.75mm] b) |- (b3-edge.west);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\tikzset{
    clockborder/.style = { 
        trapezium, trapezium angle=60, minimum width=1cm, draw, very thick
    },
    Clock/.pic = {
        \node [clockborder, shape border rotate=-180](-clockedge){#1};
        \draw[very thick] (-clockedge.east) -- ++(2cm, 0cm);
        \def\sft{0.5}
        \foreach \x in {0, 0.5, 1, 1.5}{
            \draw[very thick] (\x + \sft, 0.1) -| ++(0.25cm, 0.25cm) -| ++ (0.25cm, -0.25cm);
        }
    },
}

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\normalsize}]
        % Place the blocks 
        \draw(-3.5, 0) pic (gen) {Component={Sinewave\\Generator}{t}};
        \draw pic (adder) {Component={Adder}{t}};
        \draw(3.5, 0) pic (ds) {Component={ODESystem}{t}};
        \draw(7, 1.5) pic (writer) {Component={Writer}{t}};
        \draw(2, -2.25) pic (memory) {Component={Memory}{t}};
        % Glow the blocks
        \drawshadowbis{gen-edge};
        \drawshadowbis{adder-edge};
        \drawshadowbis{ds-edge};
        \drawshadowbis{writer-edge};
        \drawshadowbis{memory-edge};
        \begin{scope}[line width=1.5mm, ->, >={Triangle[width=3mm,length=3mm]}]
            \draw[-] ([yshift=2mm] gen-edge.east) -- ++(1cm, 0cm) node[midway, anchor=south]{$r(t)$} coordinate(d); 
            \draw (d) -- ([yshift=2mm]  adder-edge.west);
            \draw (adder-edge.east) -- node[midway, anchor=south]{$u(t)$} (ds-edge.west);
            \draw[-] (ds-edge.east) -- ++(1cm, 0cm) node[midway, anchor=south]{$y(t)$} coordinate (a);
            \draw (a) |- ([yshift=-3mm] writer-edge.west);
            \draw (a) |- (memory-edge.east);
            \draw[-] (memory-edge.west) -- ++(-2.5cm, 0cm) coordinate (c);
            \draw ([yshift=-0.75mm] c) |- ([yshift=-2mm] adder-edge.west);
            \draw (d) |- ([yshift=3mm] writer-edge.west);
        \end{scope}
        \draw[very thick, dashed] (-5, 3) rectangle (8.5, -4);
        \node at (7.5, -3.5) {Model};

         % \Place clock 
        \begin{scope}[shift={(-4.25cm, -3.25cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

    \end{tikzpicture}
\end{document}
